Contextual Combinatorial Cascading Bandits

### 2016-01-22 contextual combinatorial cascading bandits.tex
change movielens results with bigger T

\begin{figure}
	\centering
	\subfigure[$\gamma = 1$]{
		\includegraphics[height = 3cm, width = 3.95 cm]{movie-T10000-L100-K4-1.eps}}
	\subfigure[$\gamma = 0.95$]{
		\includegraphics[height = 3cm, width = 3.95 cm]{movie-T10000-L100-K4-95.eps}}
	\caption{MovieLens}
	\label{fig:movielens} % 用于交叉引用
\end{figure}

>>>>

\begin{figure}
	\centering
	\subfigure[$\gamma = 1$]{
		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-1.eps}}
	\subfigure[$\gamma = 0.9$]{
		\includegraphics[height = 3cm, width = 3.95 cm]{movieT30000-L200-K4-9.eps}}
	\caption{MovieLens}
	\label{fig:movielens} % 用于交叉引用
\end{figure}
